Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-02 PandaEvolution.tex

Given the communication requirements of PanDA Pilots and the unused capacity of
Titan, PanDA pilot was repurposed to serve as a job broker on the DTN nodes of
Titan. Maintaining the core modules of PanDA Pilot and its stand-alone
architecture, this prototype called `PanDA Broker' implements functionalities
to: (i) interrogate Titan about backfill availability; (ii) pull MC jobs and
events; (iii) wrap the payload of ATLAS jobs into MPI scripts; (iv) submitting
MPI scripts to Titan's PBS batch system and monitor their execution; and (v)
staging input/output files. Backfill querying, payload wrapping, and scripts
submission required a new implementation while pulling ATLAS job and events, and
file staging were inherited from PanDA Pilot.

@@

Once deployed on Titan, every PanDA Broker supports the execution of MC detector
simulation in 8 steps: (i) PanDA Broker queries Titan's Moab scheduler about
current backfill availability; (ii) the PanDA Broker queries the Job Dispatcher
module of the PanDA server for ATLAS jobs that have been bound to Titan by JEDI;
(iii) Upon receiving the descriptions of those jobs, PanDA Broker pulls their
input files from the ATLAS DDM service to the DTN; (iv) the PanDA Broker creates
an MPI script, wrapping enough ATLAS jobs' payload to fit backfill availability;
(v) the PanDA Broker submits the MPI script to the Titan's PBS batch system via
RADICAL-SAGA; (vi) upon execution on the worker node(s), the MPI script creates
configures and executes one AthenaMP for each work node available; (vi) AthenaMP
spawns 1 event simulation process on each available core (16); (vii) during
execution, PanDA Broker monitors execution progress and sends PanDA Server
``heart beats'' for each job.; and (viii) upon completion of each simulation,
the PanDA Broker locates the output on the shared filesystem, transfer it to
designated computing centre, and performs cleanup.

\mtnote{Address Alexei's comments: Add a paragraph explaining how this solution has been ported to other HPC machines and reference relevant publications.}

>>>>

Given the communication requirements of PanDA Pilots and the unused capacity of
Titan, PanDA pilot was repurposed to serve as a job broker on the DTN nodes of
Titan (Fig.~\ref{fig:panda_broker}). Maintaining the core modules of PanDA Pilot
and its stand-alone architecture, this prototype called `PanDA Broker'
implements functionalities to: (i) interrogate Titan about backfill
availability; (ii) pull MC jobs and events; (iii) wrap the payload of ATLAS jobs
into MPI scripts; (iv) submitting MPI scripts to Titan's PBS batch system and
monitor their execution; and (v) staging input/output files. Backfill querying,
payload wrapping, and scripts submission required a new implementation while
pulling ATLAS job and events, and file staging were inherited from PanDA Pilot.

@@

Once deployed on Titan, every PanDA Broker supports the execution of MC detector
simulation in 9 steps. PanDA Broker queries the Job Dispatcher module of the
PanDA server for ATLAS jobs that have been bound to Titan by JEDI
(Fig.~\ref{fig:panda_broker}:1). Upon receiving jobs descriptions, PanDA Broker
pulls jobs' input files from the ATLAS DDM service to the OLCF Lustre file
system (Fig.~\ref{fig:panda_broker}:3). PanDA Broker queries Titan's Moab
scheduler about current backfill availability (Fig.~\ref{fig:panda_broker}:2)
and creates an MPI script, wrapping enough ATLAS jobs' payload to fit backfill
availability. PanDA Broker submits the MPI script to the Titan's Torque batch
system via RADICAL-SAGA (Fig.~\ref{fig:panda_broker}:4).

Upon execution on the worker node(s) (Fig.~\ref{fig:panda_broker}:5), the MPI
script initializes and configures the execution environment
(Fig.~\ref{fig:panda_broker}:6), and executes one AthenaMP for each available
work node (Fig.~\ref{fig:panda_broker}:7). AthenaMP retrieves events from Lustre
(Fig.~\ref{fig:panda_broker}:8) and spawns 1 event simulation process on each of
the 16 available cores (Fig.~\ref{fig:panda_broker}:9).
% During execution, PanDA Broker monitors execution progress and sends PanDA
% Server ``heart beats'' for each job.; and (viii)
Upon completion of each MPI script, PanDA Broker transfer the jobs' output to
designated computing centre via the ATLAS DDM(Fig.~\ref{fig:panda_broker}:10),
and performs cleanup.

\mtnote{Address Alexei's comments: Add a paragraph explaining how this solution
has been ported to other HPC machines and reference relevant publications.}
While PanDA Broker implementation is resource specific, it was successfully
ported also to other supercomputers, including the Ansel (?) at \ldots and
\ldots at the National Energy Research Scientific Computing Center (NERSC).
